\cvsection{Career History}
\begin{cventries}
  \cventry
    {MIRRIAD}
    {API software engineer}
    {2017 $\sim$ Pres.}
    {London}
    {
      \begin{cvitems}
        \item {Led the product requirements review, estimation, prototyping, and implementation for the asynchronous API to the company's novel native in-video advertising technique.}
        \item {Led building automated system integration tests written in ubiquitous language from scratch with pipelines built in CI, which cover all micro services around the life cycle of video processing end to end. Improved feature coverage from only GUI to all server behavior.}
        \item {Led the design and implementation of API gateway over the native brand embedding component in asynchronous manner. Migrated desktop software functions to cloud based, highly scalable and low latency endpoints powered by heterogeneous micro services.}
        \item {Designed and built micro service to aggregate and provide enriched metadata for video processing jobs in backend, with CSP coroutine modal allowing large throughput and high concurrency in data persistence, progress reporting and statistic analysis.}
        \item {Built DevOps tools to facilitate service deployments, build cross-platform, and validate messaging endpoints etc.}
        \item {Implemented messaging library extending STOMP protocol serving Python components to provide advanced features like connection reestablishment, JMS map message type support etc.}
        \item {Led the drafting of logging scandalization across R\&D department and API invoking tracking mechanism from end to end. Built a modern logging library for C++ project and integrated log shipping from service in C++ and Python to ELK for analysis and visualization.}
      \end{cvitems}
    }
    \begin{flushleft}
    \entrypositionstyle{Techniques:\\}
    \descriptionstyle{Micro service, Cloud Computing, AWS, Tencent Cloud, Python, C++, GIT, Docker, ActiveMQ, Terraform, Vault, Bamboo\&JIRA, ELK, Agile}
    \end{flushleft}

  \cventry
    {CISCO}
    {Software engineer}
    {2010 $\sim$ 2017}
    {Chandler's Ford}
    {}
  \cventryX
    {- System Integrator}
    {2016 $\sim$ 2017}
    {Diagnose, investigate and integrate features and issues for the next generation of digital TV broadcasting system of SKY Europe with 22.4 million subscribers. Scrub JIRA tickets from various stakeholders, prioritize and build backlog in daily basis. Reproduce issues, seek root causes, build solutions, and manage life cycle of tickets. Be responsible and discuss with end customers directly.}
    {
      \begin{cvitems}
        \item {Performed fast and well targeted analysis in end to end scale on full stack from applications down to Linux kernels and drivers through over 50 software components across three variant projects (UK, Germany and Italy).}
        \item {Close to 100\% accuracy in diagnostics over hundreds of issues went through in the last 6 months.}
      \end{cvitems}
    }
  \cventryX
    {- Full Stack Developer}
    {2010 $\sim$ 2016}
    {Design, develop and test features in scrum team in full stack scale for industry leading product deployed to 5 million subscribers of SKY Deutschland. Maintain the embedded system covering drivers, middleware and up to EPG application.}
    % {including an Electronic Programme Guide application, drivers over digital tuners, DEMUX/REMUX and HDMI etc., and a multi-process, real-time middleware running on embedded Linux to receive, decode and display broadcasted metadata and digital video/audio.}
    {
      \begin{cvitems}
        \item {Implemented features like DVB scanning, LED control, HDCP/HDR/10bit color depth info. rendering, http API and EPG.}
        \item {Coached teams with Test Driven Development methodology and successfully applied to daily development. }
        \item {Supported 60 heads team as Coverity coach since 2016. Led setting up static analysis process, integration to build system and Jenkins pipeline maintenance. Over 300 high impacted security related defects were exposed with Coverity scan and the number was reduced to lower than 100 with follow-on actions, and no new defects raised.}
      \end{cvitems}
    }
    \begin{flushleft}
    \entrypositionstyle{Techiniques:\\}
    \descriptionstyle{Embedded device, Busybox, Broadcom/ST chipsets, UART, DVB, MPEG, DTV, OTT, UHD, HDR, VOD, PDL, DASH, HDCP, C/C++, Python, Bash, Actionscript, GIT, Docker, Jenkins, ClearCase, ClearQuest, Oracle ALM, Agile, Rally, JIRA, TDD, BDD, MISRA, Coverity, KLOCWORK}
    \end{flushleft}
\end{cventries}
